Staged Abstract Interpreters

### 2019-04-06 paper/70_eval.tex
wip evaluation

We use Scala 2.12.7 and Oracle JVM 1.8.0-191, running on an Ubuntu 16.04 LTS
(kernel 4.4.0) machine. All of our evaluations were performed on a machine with 4 Intel
Xeon Platinum 8168 CPU at 2.7GHz and 3 TiB of RAM. Although the machine has 96
cores (192 threads) in total, the abstract interpreters are single-threaded.
To minimize the effect of warming-up from the JVM JIT compiler, all the
experiments are executed for 20 times and we report the statistical median value
of the running times (in seconds).

@@

\begin{figure}[h]
\footnotesize
\begin{tabular}{@{}lllll@{}}
\toprule
    program             &\#AST & unstaged   & staged     & $\frac{\text{unstaged}}{\text{staged}}$ \\ \midrule
    @fib@               & 32   & 0.013      & 0.002      & 650.00\%          \\
    @rsa@               & 451  & 0.232      & 0.042      & 552.38\%          \\
    @church@            & 120  & 67.342     & 18.917     & 355.99\%          \\
    @fermat@            & 310  & 0.024      & 0.004      & 600.00\%          \\
    @mbrotZ@            & 331  & 0.763      & 0.127      & 600.79\%          \\
    @lattice@           & 609  & 31.874     & 8.816      & 361.59\%          \\
    @kcfa-worst-16@     & 182  & 0.045      & 0.006      & 750.00\%          \\
    @kcfa-worst-32@     & 358  & 0.284      & 0.022      & 1290.91\%         \\
    @kcfa-worst-64@     & 774  & 2.18       & 0.129      & 1689.92\%         \\
    @solovay-strassen@  & 523  & 5.094      & 1.189      & 428.43\%          \\
    \bottomrule
\end{tabular}
\caption{Evaluation result for 0CFA without store-widening.} \label{evaluation_result}
\end{figure}

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on 0CFA without store-widening. The
\textit{unstaged} and \textit{staged} columns show the median time to finish the
analysis (in seconds). The last column $\frac{\text{unstaged}}{\text{staged}}$
shows the improvement from staging. \todo{0cfa, 1cfa, store-widen}
As we can see from the table, the staged version significantly outperforms the
unstaged version on all benchmarks, especially for the @kcfa-worst-@$n$ series.
We observe the most improvement of 17x times faster than the unstaged version on
@kcfa-worst-64@. On average, the staging produces code that runs 7x times faster
than the unstaged analyzer.

>>>>

We use Scala 2.12.7 and Oracle JVM 1.8.0-191, running on an Ubuntu 16.04 LTS
(kernel 4.4.0) machine. All of our evaluations were performed on a machine with 4 Intel
Xeon Platinum 8168 CPU at 2.7GHz and 3 TiB of RAM. Although the machine has 96
cores (192 threads) in total, the abstract interpreters are single-threaded.
To minimize the effect of warming-up from the JVM JIT compiler, all the
experiments are executed for 20 times and we report the statistical median value
of the running times. We set a 5 minutes timeout.

@@

\begin{figure}[h]
\footnotesize
\begin{tabular}{@{}ll|lll|lll@{}}
\toprule
    program             &\#AST & unstaged   & staged     & $\frac{\text{unstaged}}{\text{staged}}$ & unstaged   & staged    & $\frac{\text{unstaged}}{\text{staged}}$  \\ 
    \midrule
                        &      & \multicolumn{3}{c}{w/o store-widening} &  \multicolumn{3}{c}{w/ store-widening}  \\
    \midrule
    @fib@               & 32   & 0.013      & 0.002      & 650.00\%  & & &        \\
    @rsa@               & 451  & 0.232      & 0.042      & 552.38\%  & & &        \\
    @church@            & 120  & 67.342     & 18.917     & 355.99\%  & & &        \\
    @fermat@            & 310  & 0.024      & 0.004      & 600.00\%  & & &        \\
    @mbrotZ@            & 331  & 0.763      & 0.127      & 600.79\%  & & &        \\
    @lattice@           & 609  & 31.874     & 8.816      & 361.59\%  & & &       \\
    @kcfa-worst-16@     & 182  & 0.045      & 0.006      & 750.00\%  & & &      \\
    @kcfa-worst-32@     & 358  & 0.284      & 0.022      & 1290.91\% & & &      \\
    @kcfa-worst-64@     & 774  & 2.18       & 0.129      & 1689.92\% & & &      \\
    @solovay-strassen@  & 523  & 5.094      & 1.189      & 428.43\%  & & &       \\
    @regex@             & 550  & -          & -          & -         & & &       \\
    @matrix@            & 1891 & -          & -          & -         & & &       \\
    \bottomrule
\end{tabular}
\caption{Evaluation result for monovariant control-flow analysis.} \label{evaluation_result}
\end{figure}

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on 0CFA without store-widening. The
\textit{unstaged} and \textit{staged} columns show the median time to finish the
analysis (in seconds). The last column $\frac{\text{unstaged}}{\text{staged}}$
shows the improvement from staging. The dash - in some cells indicates timeout.
\todo{0cfa, 1cfa, store-widen}
As we can see from the table, the staged version significantly outperforms the
unstaged version on all benchmarks, especially for the @kcfa-worst-@$n$ series.
We observe the most improvement of 17x times faster than the unstaged version on
@kcfa-worst-64@. On average, the staging produces code that runs 7x times faster
than the unstaged analyzer.
